On Solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization by greedy methods and their hybridizations

### 2020-10-03 doc/paper.tex
Section 2
description of benchmarks

      In order to solve this model, we apply a general purpose solver \textsc{Cplex}.
       \subsection{Constraint programming method}\fxnote{TODO: Marko}

     \section{Algorithmic Approaches for WOAGP}
     \subsection{Greedy approaches for solving WOAGP}
      Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance and then
          apply greedy algorithms to solve WOAGP. These algorithms produce a solution of reasonable quality within a short interval of time. Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. Among all candidates (solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value until the solution is complete (i.e., cover all  points from $D(P)$).
          A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

@@

     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$  as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
       	  \item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	 \item \emph{distance-based benchmarks:} For each vertex $i$, a weight is assigned to $i$ by making use of the information about the distance from that point to the point in the polygon which is at the longest distance but visible from $i$ (among all other points in polygon).
       	 \item \emph{point-based benchmarks:} For each vertex $j$, we are looking for the number of points in D(P) that are visible from the given vertex $(|V(j)|)$. Based on this measure, we assign prices to the vertices. If |V(j)| is larger, the large is the price of the vertex $j$.
       \end{itemize}
     \section{Conclusions and Future Work}

>>>>

      In order to solve this model, we apply a general purpose solver \textsc{Cplex}.
       \subsection{Constraint programming method} An equivalent CP model was implemented and tested by CP Optimizer. In this case,  Constraint~(\ref{eq:const-3}) is transformed into 
       \begin{equation}
           \bigvee_{ j \in V } (a_{ij} \wedge x_j) = 1, 
       \end{equation}
      whereas the other constraints and the objective function are the same like in the above MIP model. 
     \section{Algorithmic Approaches for WOAGP}
     \subsection{Greedy approaches for solving WOAGP}
      Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance and then
          apply greedy algorithms to solve WOAGP. These algorithms produce a solution of reasonable quality within a short interval of time. Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. Among all candidates (solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value until the solution is complete (i.e., cover all  points from $D(P)$).
          A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

@@

     \section{Computational Results}
       We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
       \begin{itemize}
       	  \item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	 \item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
       	 \begin{equation}
       	   w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n. 
       	 \end{equation}
       \end{itemize}
     \section{Conclusions and Future Work}
